Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2023-12-12 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
After our work together

output:
  rticles::ieee_article:
    number_sections: TRUE
    #citation_package: biblatex
    citation_package: natbib

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
#library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)

@@

>>>>

output:
  rticles::ieee_article:
    number_sections: TRUE
    citation_package: natbib

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
#library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)

@@

\textcolor{red}{Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
We work with non-parametric estimators of the entropy, we reduce the bias of those based on spacings using bootstrap, and select the best ones.
Next, we study the empirical distribution of these estimators under the null hypothesis, followed by a study of the size and power of the proposed test.
We conclude the study with applications to SAR data.}
